The Importance of Initial Conditions in Seasonal Predictions of Antarctic Sea Ice

### 2025-11-19 analysis/paper/access-ice.tex
Renders

The underlying code for this study is available on GitHub and can be
accessed via this link https://github.com/eliocamp/access-s2\_ice-eval.

Raw data of ACCESS-S1 and ACCESS-S2 forecasts are not available due to
size. Derived datasets required to reproduce the results are available
in this Zenodo repository: https://zenodo.org/records/17479538
\citep{campitelli2025}

>>>>

The underlying code for this study is available on GitHub:
https://github.com/eliocamp/access-s2\_ice-eval.

Raw data of ACCESS-S1 and ACCESS-S2 hindcast are not available due to
size. Derived datasets required to reproduce the results, including
extent timeseries and error measures, are available in this Zenodo
repository: https://zenodo.org/records/17479538 \citep{campitelli2025}

\section{Competing interests}\label{competing-interests}

All authors declare no financial or non-financial competing interests.

\section{Author contributions}\label{author-contributions}

EC performed the data analysis and wrote the manuscript draft. AP, JA,
EL, MW and PR, performed interpretation of the results, and reviewed and
edited the draft. All authors read and approved the final manuscript.
